---
title: "Knapsack experiments"
authors: "Sydney Richards and Sophia Mitchellette"
date: "October 31, 2016"
output: html_document
---
// 1 random_restart_cliff_score_10_1000_3_DataSet
```{r}
data_cliff_10_1000_3 <- read.csv("../data/random_restart_cliff_score_10_1000_3_DataSet.txt", sep="")
```

```{r, echo=FALSE}
plot(data_cliff_10_1000_3$Score ~ data_cliff_10_1000_3$Search_method,
     xlab="Searcher", ylab="Score")
```


// 2 random_restart_cliff_score_10_1000_5_DataSet
```{r}
data_cliff_10_1000_5 <- read.csv("../data/random_restart_cliff_score_10_1000_5_DataSet.txt", sep="")
```

```{r, echo=FALSE}
plot(data_cliff_10_1000_5$Score ~ data_cliff_10_1000_5$Search_method,
     xlab="Searcher", ylab="Score")
```


// 3 random_restart_cliff_score_30_1000_3_DataSet
```{r}
data_cliff_30_1000_3 <- read.csv("../data/random_restart_cliff_score_30_1000_3_DataSet.txt", sep="")
```

```{r, echo=FALSE}
plot(data_cliff_30_1000_3$Score ~ data_cliff_30_1000_3$Search_method,
     xlab="Searcher", ylab="Score")
```


// 4 random_restart_cliff_score_30_1000_5_DataSet
```{r}
data_cliff_30_1000_5 <- read.csv("../data/random_restart_cliff_score_30_1000_5_DataSet.txt", sep="")
```

```{r, echo=FALSE}
plot(data_cliff_30_1000_5$Score ~ data_cliff_30_1000_5$Search_method,
     xlab="Searcher", ylab="Score")
```


// 5 random_restart_cliff_score_30_1000_20_DataSet
```{r}
data_cliff_30_1000_20 <- read.csv("../data/random_restart_cliff_score_30_1000_20_DataSet.txt", sep="")
```

```{r, echo=FALSE}
plot(data_cliff_30_1000_20$Score ~ data_cliff_30_1000_20$Search_method,
     xlab="Searcher", ylab="Score")
```

// 6 random_restart_cliff_score_60_1000_5_DataSet
```{r}
data_cliff_60_1000_5 <- read.csv("../data/random_restart_cliff_score_60_1000_5_DataSet.txt", sep="")
```

```{r, echo=FALSE}
plot(data_cliff_60_1000_5$Score ~ data_cliff_60_1000_5$Search_method,
     xlab="Searcher", ylab="Score")
```

// 7 random_restart_cliff_score_60_1000_20_DataSet
```{r}
data_cliff_60_1000_20 <- read.csv("../data/random_restart_cliff_score_60_1000_20_DataSet.txt", sep="")
```

```{r, echo=FALSE}
plot(data_cliff_60_1000_20$Score ~ data_cliff_60_1000_20$Search_method,
     xlab="Searcher", ylab="Score")
```


// 8 random_restart_penalized_score_10_1000_3_DataSet

```{r}
data_penalized_10_1000_3 <- read.csv("../data/random_restart_penalized_score_10_1000_3_DataSet.txt", sep="")

plot(data_penalized_10_1000_3$Score ~ data_penalized_10_1000_3$Search_method,
     xlab="Searcher", ylab="Score")
```

```{r}
data_penalized_10_1000_3$Non_negative_score = ifelse(data_penalized_10_1000_3$Score<0, 0, data_penalized_10_1000_3$Score)

plot(data_penalized_10_1000_3$Non_negative_score ~ data_penalized_10_1000_3$Search_method,
     xlab="Searcher", ylab="Score")
```

```{r}
pairwise.wilcox.test(data_penalized_10_1000_3$Non_negative_score, data_penalized_10_1000_3$Search_method)
```

```{r}
library("ggplot2")
```

```{r}
twenty_item_problems = subset(data_penalized_10_1000_3, Problem=="knapPI_11_20_1000_4" | Problem=="knapPI_13_20_1000_4" | Problem=="knapPI_16_20_1000_4")

ggplot(twenty_item_problems, aes(Search_method, Non_negative_score)) + geom_boxplot() + facet_grid(. ~ Problem)

two_hundren_item_problems = subset(data_penalized_10_1000_3, Problem=="knapPI_11_200_1000_4" | Problem=="knapPI_13_200_1000_4" | Problem=="knapPI_16_200_1000_4")

ggplot(two_hundren_item_problems, aes(Search_method, Non_negative_score)) + geom_boxplot() + facet_grid(. ~ Problem)
```

```{r}
ggplot(twenty_item_problems, aes(Search_method, Non_negative_score)) + geom_boxplot() + facet_grid(. ~ Max_evals)

ggplot(two_hundren_item_problems, aes(Search_method, Non_negative_score)) + geom_boxplot() + facet_grid(. ~ Max_evals)
```

```{r}
ggplot(twenty_item_problems, aes(factor(Max_evals), Non_negative_score)) + geom_boxplot() + facet_grid(Problem ~ Search_method)

ggplot(two_hundren_item_problems, aes(factor(Max_evals), Non_negative_score)) + geom_boxplot() + facet_grid(Problem ~ Search_method)
```

```{r}
pairwise.wilcox.test(data_penalized_10_1000_3$Non_negative_score, interaction(data_penalized_10_1000_3$Search_method, data_penalized_10_1000_3$Problem, data_penalized_10_1000_3$Max_evals))
```

```{r}
library("rpart")
library("rpart.plot")

rp <- rpart(Non_negative_score ~ Search_method + Problem + Max_evals, data=data_penalized_10_1000_3)
rp
rpart.plot(rp)
```

// 9 random_restart_penalized_score_10_1000_5_DataSet

```{r}
data_penalized_10_1000_5 <- read.csv("../data/random_restart_penalized_score_10_1000_5_DataSet.txt", sep="")

plot(data_penalized_10_1000_5$Score ~ data_penalized_10_1000_5$Search_method,
     xlab="Searcher", ylab="Score")
```

```{r}
data_penalized_10_1000_5$Non_negative_score = ifelse(data_penalized_10_1000_5$Score<0, 0, data_penalized_10_1000_5$Score)

plot(data_penalized_10_1000_5$Non_negative_score ~ data_penalized_10_1000_5$Search_method,
     xlab="Searcher", ylab="Score")
```

```{r}
pairwise.wilcox.test(data_penalized_10_1000_5$Non_negative_score, data_penalized_10_1000_5$Search_method)
```

```{r}
library("ggplot2")
```

```{r}
twenty_item_problems = subset(data_penalized_10_1000_5, Problem=="k_11_20_4" | Problem=="k_13_20_4" | Problem=="k_16_20_4")

ggplot(twenty_item_problems, aes(Search_method, Non_negative_score)) + geom_boxplot() + facet_grid(. ~ Problem)

two_hundren_item_problems = subset(data_penalized_10_1000_5, Problem=="k_11_200_4" | Problem=="k_13_200_4" | Problem=="k_16_200_4")

ggplot(two_hundren_item_problems, aes(Search_method, Non_negative_score)) + geom_boxplot() + facet_grid(. ~ Problem)
```

```{r}
ggplot(twenty_item_problems, aes(Search_method, Non_negative_score)) + geom_boxplot() + facet_grid(. ~ Max_evals)

ggplot(two_hundren_item_problems, aes(Search_method, Non_negative_score)) + geom_boxplot() + facet_grid(. ~ Max_evals)
```

```{r}
ggplot(twenty_item_problems, aes(factor(Max_evals), Non_negative_score)) + geom_boxplot() + facet_grid(Problem ~ Search_method)

ggplot(two_hundren_item_problems, aes(factor(Max_evals), Non_negative_score)) + geom_boxplot() + facet_grid(Problem ~ Search_method)
```

```{r}
pairwise.wilcox.test(data_penalized_10_1000_5$Non_negative_score, interaction(data_penalized_10_1000_5$Search_method, data_penalized_10_1000_5$Problem, data_penalized_10_1000_5$Max_evals))
```

```{r}
library("rpart")
library("rpart.plot")

rp <- rpart(Non_negative_score ~ Search_method + Problem + Max_evals, data=data_penalized_10_1000_5)
rp
rpart.plot(rp)
```

// 10 random_restart_penalized_score_30_1000_3_DataSet

```{r}
data_penalized_30_1000_3 <- read.csv("../data/random_restart_penalized_score_30_1000_3.txt", sep="")

plot(data_penalized_30_1000_3$Score ~ data_penalized_30_1000_3$Search_method,
     xlab="Searcher", ylab="Score")
```

```{r}
data_penalized_30_1000_3$Non_negative_score = ifelse(data_penalized_30_1000_3$Score<0, 0, data_penalized_30_1000_3$Score)

plot(data_penalized_30_1000_3$Non_negative_score ~ data_penalized_30_1000_3$Search_method,
     xlab="Searcher", ylab="Score")
```

```{r}
pairwise.wilcox.test(data_penalized_30_1000_3$Non_negative_score, data_penalized_30_1000_3$Search_method)
```

```{r}
library("ggplot2")
```

```{r}
twenty_item_problems = subset(data_penalized_30_1000_3, Problem=="k_11_20_4" | Problem=="k_13_20_4" | Problem=="k_16_20_4")

ggplot(twenty_item_problems, aes(Search_method, Non_negative_score)) + geom_boxplot() + facet_grid(. ~ Problem)

two_hundren_item_problems = subset(data_penalized_30_1000_3, Problem=="k_11_200_4" | Problem=="k_13_200_4" | Problem=="k_16_200_4")

ggplot(two_hundren_item_problems, aes(Search_method, Non_negative_score)) + geom_boxplot() + facet_grid(. ~ Problem)
```

```{r}
ggplot(twenty_item_problems, aes(Search_method, Non_negative_score)) + geom_boxplot() + facet_grid(. ~ Max_evals)

ggplot(two_hundren_item_problems, aes(Search_method, Non_negative_score)) + geom_boxplot() + facet_grid(. ~ Max_evals)
```

```{r}
ggplot(twenty_item_problems, aes(factor(Max_evals), Non_negative_score)) + geom_boxplot() + facet_grid(Problem ~ Search_method)

ggplot(two_hundren_item_problems, aes(factor(Max_evals), Non_negative_score)) + geom_boxplot() + facet_grid(Problem ~ Search_method)
```

```{r}
pairwise.wilcox.test(data_penalized_30_1000_3$Non_negative_score, interaction(data_penalized_30_1000_3$Search_method, data_penalized_30_1000_3$Problem, data_penalized_30_1000_3$Max_evals))
```

```{r}
library("rpart")
library("rpart.plot")

rp <- rpart(Non_negative_score ~ Search_method + Problem + Max_evals, data=data_penalized_30_1000_3)
rp
rpart.plot(rp)
```


// 11 random_restart_penalized_score_30_1000_5_DataSet

```{r}
data_penalized_30_1000_5 <- read.csv("../data/random_restart_penalized_score_30_1000_5_DataSet.txt", sep="")

plot(data_penalized_30_1000_5$Score ~ data_penalized_30_1000_5$Search_method,
     xlab="Searcher", ylab="Score")
```

```{r}
data_penalized_30_1000_5$Non_negative_score = ifelse(data_penalized_30_1000_5$Score<0, 0, data_penalized_30_1000_5$Score)

plot(data_penalized_30_1000_5$Non_negative_score ~ data_penalized_30_1000_5$Search_method,
     xlab="Searcher", ylab="Score")
```

```{r}
pairwise.wilcox.test(data_penalized_30_1000_5$Non_negative_score, data_penalized_30_1000_5$Search_method)
```

```{r}
library("ggplot2")
```

```{r}
twenty_item_problems = subset(data_penalized_30_1000_5, Problem=="k_11_20_4" | Problem=="k_13_20_4" | Problem=="k_16_20_4")

ggplot(twenty_item_problems, aes(Search_method, Non_negative_score)) + geom_boxplot() + facet_grid(. ~ Problem)

two_hundren_item_problems = subset(data_penalized_30_1000_5, Problem=="k_11_200_4" | Problem=="k_13_200_4" | Problem=="k_16_200_4")

ggplot(two_hundren_item_problems, aes(Search_method, Non_negative_score)) + geom_boxplot() + facet_grid(. ~ Problem)
```

```{r}
ggplot(twenty_item_problems, aes(Search_method, Non_negative_score)) + geom_boxplot() + facet_grid(. ~ Max_evals)

ggplot(two_hundren_item_problems, aes(Search_method, Non_negative_score)) + geom_boxplot() + facet_grid(. ~ Max_evals)
```

```{r}
ggplot(twenty_item_problems, aes(factor(Max_evals), Non_negative_score)) + geom_boxplot() + facet_grid(Problem ~ Search_method)

ggplot(two_hundren_item_problems, aes(factor(Max_evals), Non_negative_score)) + geom_boxplot() + facet_grid(Problem ~ Search_method)
```

```{r}
pairwise.wilcox.test(data_penalized_30_1000_5$Non_negative_score, interaction(data_penalized_30_1000_5$Search_method, data_penalized_30_1000_5$Problem, data_penalized_30_1000_5$Max_evals))
```

```{r}
library("rpart")
library("rpart.plot")

rp <- rpart(Non_negative_score ~ Search_method + Problem + Max_evals, data=data_penalized_30_1000_5)
rp
rpart.plot(rp)
```

// 12 random_restart_penalized_score_30_1000_20_DataSet

```{r}
data_penalized_30_1000_20 <- read.csv("../data/random_restart_penalized_score_30_1000_20_DataSet.txt", sep="")

plot(data_penalized_30_1000_20$Score ~ data_penalized_30_1000_20$Search_method,
     xlab="Searcher", ylab="Score")
```

```{r}
data_penalized_30_1000_20$Non_negative_score = ifelse(data_penalized_30_1000_20$Score<0, 0, data_penalized_30_1000_20$Score)

plot(data_penalized_30_1000_20$Non_negative_score ~ data_penalized_30_1000_20$Search_method,
     xlab="Searcher", ylab="Score")
```

```{r}
pairwise.wilcox.test(data_penalized_30_1000_20$Non_negative_score, data_penalized_30_1000_20$Search_method)
```

```{r}
library("ggplot2")
```

```{r}
twenty_item_problems = subset(data_penalized_30_1000_20, Problem=="k_11_20_4" | Problem=="k_13_20_4" | Problem=="k_16_20_4")

ggplot(twenty_item_problems, aes(Search_method, Non_negative_score)) + geom_boxplot() + facet_grid(. ~ Problem)

two_hundren_item_problems = subset(data_penalized_30_1000_20, Problem=="k_11_200_4" | Problem=="k_13_200_4" | Problem=="k_16_200_4")

ggplot(two_hundren_item_problems, aes(Search_method, Non_negative_score)) + geom_boxplot() + facet_grid(. ~ Problem)
```

```{r}
ggplot(twenty_item_problems, aes(Search_method, Non_negative_score)) + geom_boxplot() + facet_grid(. ~ Max_evals)

ggplot(two_hundren_item_problems, aes(Search_method, Non_negative_score)) + geom_boxplot() + facet_grid(. ~ Max_evals)
```

```{r}
ggplot(twenty_item_problems, aes(factor(Max_evals), Non_negative_score)) + geom_boxplot() + facet_grid(Problem ~ Search_method)

ggplot(two_hundren_item_problems, aes(factor(Max_evals), Non_negative_score)) + geom_boxplot() + facet_grid(Problem ~ Search_method)
```

```{r}
pairwise.wilcox.test(data_penalized_30_1000_20$Non_negative_score, interaction(data_penalized_30_1000_20$Search_method, data_penalized_30_1000_20$Problem, data_penalized_30_1000_20$Max_evals))
```

```{r}
library("rpart")
library("rpart.plot")

rp <- rpart(Non_negative_score ~ Search_method + Problem + Max_evals, data=data_penalized_30_1000_20)
rp
rpart.plot(rp)
```


// 13 random_restart_penalized_score_60_1000_5_DataSet

```{r}
data_penalized_60_1000_5 <- read.csv("../data/random_restart_penalized_score_60_1000_5_DataSet.txt", sep="")

plot(data_penalized_60_1000_5$Score ~ data_penalized_60_1000_5$Search_method,
     xlab="Searcher", ylab="Score")
```

```{r}
data_penalized_60_1000_5$Non_negative_score = ifelse(data_penalized_60_1000_5$Score<0, 0, data_penalized_60_1000_5$Score)

plot(data_penalized_60_1000_5$Non_negative_score ~ data_penalized_60_1000_5$Search_method,
     xlab="Searcher", ylab="Score")
```

```{r}
pairwise.wilcox.test(data_penalized_60_1000_5$Non_negative_score, data_penalized_60_1000_5$Search_method)
```

```{r}
library("ggplot2")
```

```{r}
twenty_item_problems = subset(data_penalized_60_1000_5, Problem=="k_11_20_4" | Problem=="k_13_20_4" | Problem=="k_16_20_4")

ggplot(twenty_item_problems, aes(Search_method, Non_negative_score)) + geom_boxplot() + facet_grid(. ~ Problem)

two_hundren_item_problems = subset(data_penalized_60_1000_5, Problem=="k_11_200_4" | Problem=="k_13_200_4" | Problem=="k_16_200_4")

ggplot(two_hundren_item_problems, aes(Search_method, Non_negative_score)) + geom_boxplot() + facet_grid(. ~ Problem)
```

```{r}
ggplot(twenty_item_problems, aes(Search_method, Non_negative_score)) + geom_boxplot() + facet_grid(. ~ Max_evals)

ggplot(two_hundren_item_problems, aes(Search_method, Non_negative_score)) + geom_boxplot() + facet_grid(. ~ Max_evals)
```

```{r}
ggplot(twenty_item_problems, aes(factor(Max_evals), Non_negative_score)) + geom_boxplot() + facet_grid(Problem ~ Search_method)

ggplot(two_hundren_item_problems, aes(factor(Max_evals), Non_negative_score)) + geom_boxplot() + facet_grid(Problem ~ Search_method)
```

```{r}
pairwise.wilcox.test(data_penalized_60_1000_5$Non_negative_score, interaction(data_penalized_60_1000_5$Search_method, data_penalized_60_1000_5$Problem, data_penalized_60_1000_5$Max_evals))
```

```{r}
library("rpart")
library("rpart.plot")

rp <- rpart(Non_negative_score ~ Search_method + Problem + Max_evals, data=data_penalized_60_1000_5)
rp
rpart.plot(rp)
```

// 14 random_restart_penalized_score_60_1000_20_DataSet

```{r}
data_50_runs <- read.csv("../data/random_restart_penalized_score_60_1000_20_DataSet.txt", sep="")

plot(data_50_runs$Score ~ data_50_runs$Search_method,
     xlab="Searcher", ylab="Score")
```

```{r}
data_50_runs$Non_negative_score = ifelse(data_50_runs$Score<0, 0, data_50_runs$Score)

plot(data_50_runs$Non_negative_score ~ data_50_runs$Search_method,
     xlab="Searcher", ylab="Score")
```

```{r}
pairwise.wilcox.test(data_50_runs$Non_negative_score, data_50_runs$Search_method)
```

```{r}
library("ggplot2")
```

```{r}
twenty_item_problems = subset(data_50_runs, Problem=="k_11_20_4" | Problem=="k_13_20_4" | Problem=="k_16_20_4")

ggplot(twenty_item_problems, aes(Search_method, Non_negative_score)) + geom_boxplot() + facet_grid(. ~ Problem)

two_hundren_item_problems = subset(data_50_runs, Problem=="k_11_200_4" | Problem=="k_13_200_4" | Problem=="k_16_200_4")

ggplot(two_hundren_item_problems, aes(Search_method, Non_negative_score)) + geom_boxplot() + facet_grid(. ~ Problem)
```

```{r}
ggplot(twenty_item_problems, aes(Search_method, Non_negative_score)) + geom_boxplot() + facet_grid(. ~ Max_evals)

ggplot(two_hundren_item_problems, aes(Search_method, Non_negative_score)) + geom_boxplot() + facet_grid(. ~ Max_evals)
```

```{r}
ggplot(twenty_item_problems, aes(factor(Max_evals), Non_negative_score)) + geom_boxplot() + facet_grid(Problem ~ Search_method)

ggplot(two_hundren_item_problems, aes(factor(Max_evals), Non_negative_score)) + geom_boxplot() + facet_grid(Problem ~ Search_method)
```

```{r}
pairwise.wilcox.test(data_50_runs$Non_negative_score, interaction(data_50_runs$Search_method, data_50_runs$Problem, data_50_runs$Max_evals))
```

```{r}
library("rpart")
library("rpart.plot")

rp <- rpart(Non_negative_score ~ Search_method + Problem + Max_evals, data=data_50_runs)
rp
rpart.plot(rp)
```
